Manuscript_Github_Pchabaudi_pir

### 2022-07-21 chapter4_results_chabaudi24h/Thesis_Github_Pchabaudi_pirAnalysis.Rmd
Rename and create chabaudi pir analysis files and update code for SBP and improved all pir heatmap figure

library('readr')
library('dplyr')
library('tidyr')
library('ggplot2')
library('DESeq2')
library("pheatmap")
library("RColorBrewer")
library('data.table')
library('gridExtra')
library('tibble')
library('stringr')
library('kableExtra')
library('viridis')
library('corrplot')
library('reshape2')
library('circlize') # for circular plots and colours
library('cluster')    # clustering algorithms
library('factoextra') # clustering algorithms & visualization
library('ggfortify') # so ggplot understands prcomp objects
library('ape') # for phylogeny plotting
library('dendextend') # for dendrogram plotting
library('readxl') # for reading in Excel spreadsheets
library('plotly')
library('scales')
library('processx') # for downloading the plotly plots
library('cowplot')
library('ComplexHeatmap')
library('ggbiplot')
library('ggpattern')

#Colour blind friendly palette
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
show_col(cbPalette)

@@

#Global save var - set to TRUE if you want to save figures.
global_save_var <- TRUE
```

@@

twentyfour_rMT <- read_csv('Pchabaudi_TPM_allBioReps.csv')

twentyfour_avgtpm <- list(
  'RMT' = list(
    tpm = read_csv('Pchabaudi_TPM_average.csv'),
    experiment = 'RMT'
  )
)

@@

combined_data_pir_ht_list <- lapply(names(twentyfour_avgtpm), 
       function(list_name){

@@

@@

                             Heatmap(
                               log2(1+combined_data_pir_ht)[pir_highest_tpm_order,],
                               cluster_rows = FALSE,
                               cluster_columns = FALSE,
                               show_row_names = FALSE,
                               name = 'log(TPM+1)', 
                               col = colorRamp2(c(0,
                                                  maxcol/4,
                                                  maxcol/2,
                                                  3*maxcol/4,
                                                  maxcol),
                                                viridis(5)),
                               na_col = 'white', 
                               border = TRUE,
                               border_gp = gpar(lwd = 0.1),
                               column_names_gp = gpar(fontsize = 10),
                               row_dend_width = unit(3, "cm"),
                               width = unit(4.5, 'cm'),
                               height = unit(7,'cm'),
                               row_title = NULL,
                               left_annotation = if(
                                 list_name %in% dplyr::first(names(combined_data_pir_ht_list))
                               ){
                                 clade_ha
                               }else{
                                 NULL
                               },
                               right_annotation = if(
                                 list_name %in% dplyr::last(names(combined_data_pir_ht_list))
                               ){
                                 anc_ha
                               }else{
                                 NULL
                               },
                               # row_split =  cir_info$SorL[match(pir_highest_tpm_order, 
                               #                                        cir_info$Geneid)],
                               column_title = paste(list_name),
                               heatmap_legend_param = list(
                                 labels_gp = gpar(fontsize = 10),
                                 title_gp = gpar(fontsize = 10,
                                                 fontface = 'bold'),
                                 at = c(0,
                                        maxcol/4,
                                        maxcol/2,
                                        3*maxcol/4,
                                        maxcol)
                               )
                             )
                           }
         )
         ht_list <- Reduce(`+`, ht_list)
         clade_lgd <- Legend(
           title = 'sub-family',
           at = labels_SorL,
           legend_gp = gpar(fill = SorL_col)
         )

>>>>

library('readr')
library('dplyr')
library('ggplot2')
library("RColorBrewer")
library('data.table')
library('tibble')
library('stringr')
library('kableExtra')
library('viridis')
library('reshape2')
library('ComplexHeatmap')
library('circlize') # for circular plots and colour

# library('DESeq2')
# library("pheatmap")
# 
# library('gridExtra')
# 
# library('corrplot')
# 
# library('cluster')    # clustering algorithms
# library('factoextra') # clustering algorithms & visualization
# library('ggfortify') # so ggplot understands prcomp objects
# library('ape') # for phylogeny plotting
# library('dendextend') # for dendrogram plotting
# library('readxl') # for reading in Excel spreadsheets
# library('plotly')
# library('scales')
# library('processx') # for downloading the plotly plots
# library('cowplot')
# 
# library('ggbiplot')
# library('ggpattern')

#Colour blind friendly palette
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

@@

#Global save var - set to TRUE if you want to save figures.
global_save_var <- FALSE
```

@@

chab_tpm.df <- read_csv('data/Pchabaudi_TPM_all.csv')

chab_tpm_avg.df <- read_csv('data/Pchabaudi_TPM_average.csv')

chab_tpm_avg.list <- list(
  'RMT' = list(
    tpm = chab_tpm_avg.df[,grepl(colnames(chab_tpm_avg.df), 
                                pattern = 'rMT|Geneid')],
    experiment = 'RMT'
  ),
  'SBP' = list(
    tpm = chab_tpm_avg.df[,grepl(colnames(chab_tpm_avg.df), 
                                pattern = 'SBP|Geneid')],
    experiment = 'SBP'
  )
)

@@

combined_data_pir_ht_list <- lapply(names(chab_tpm_avg.list), 
       function(list_name){

@@

#Need to reach into the data to find the maximum value of the log(TPM+1) for 
# the colouring in order to maintain consistency.

@@

                             Heatmap(
                               log2(1+combined_data_pir_ht)[pir_highest_tpm_order,],
                               cluster_rows = FALSE,
                               cluster_columns = FALSE,
                               show_row_names = FALSE,
                               name = 'log(TPM+1)', 
                               col = colorRamp2(c(0,
                                                  maxcol/4,
                                                  maxcol/2,
                                                  3*maxcol/4,
                                                  maxcol),
                                                viridis(5)),
                               na_col = 'white', 
                               border = TRUE,
                               border_gp = gpar(lwd = 0.1),
                               column_names_gp = gpar(fontsize = 10),
                               row_dend_width = unit(3, "cm"),
                               width = unit(4.5, 'cm'),
                               height = unit(7,'cm'),
                               row_title = NULL,
                               split = clade_info,
                               left_annotation = if(
                                 list_name %in% dplyr::first(names(combined_data_pir_ht_list))
                               ){
                                 clade_ha
                               }else{
                                 NULL
                               },
                               right_annotation = if(
                                 list_name %in% dplyr::last(names(combined_data_pir_ht_list))
                               ){
                                 anc_ha
                               }else{
                                 NULL
                               },
                               # row_split =  cir_info$SorL[match(pir_highest_tpm_order, 
                               #                                        cir_info$Geneid)],
                               column_title = paste(list_name),
                               heatmap_legend_param = list(
                                 labels_gp = gpar(fontsize = 10),
                                 title_gp = gpar(fontsize = 10,
                                                 fontface = 'bold'),
                                 at = c(0,
                                        maxcol/4,
                                        maxcol/2,
                                        3*maxcol/4,
                                        maxcol)
                               )
                             )
                           }
         )
         ht_list <- Reduce(`+`, ht_list)
         clade_lgd <- Legend(
           title = 'sub-family',
           at = labels_SorL,
           legend_gp = gpar(fill = SorL_col)
         )

### 2022-07-21 chapter4_results_chabaudi24h/old_Pchabaudi24h/Manuscript_Github_Pchabaudi_pir.Rmd
Rename and create chabaudi pir analysis files and update code for SBP and improved all pir heatmap figure

library('readr')
library('dplyr')
library('tidyr')
library('ggplot2')
library('DESeq2')
library("pheatmap")
library("RColorBrewer")
library('data.table')
library('gridExtra')
library('tibble')
library('stringr')
library('kableExtra')
library('viridis')
library('corrplot')
library('reshape2')
library('circlize') # for circular plots and colours
library('cluster')    # clustering algorithms
library('factoextra') # clustering algorithms & visualization
library('ggfortify') # so ggplot understands prcomp objects
library('ape') # for phylogeny plotting
library('dendextend') # for dendrogram plotting
library('readxl') # for reading in Excel spreadsheets
library('plotly')
library('scales')
library('processx') # for downloading the plotly plots
library('cowplot')
library('ComplexHeatmap')
library('ggbiplot')
library('ggpattern')

>>>>

library('readr')
library('dplyr')
library('ggplot2')
library("RColorBrewer")
library('data.table')
library('tibble')
library('stringr')
library('kableExtra')
library('viridis')
library('reshape2')

# library('DESeq2')
# library("pheatmap")
# 
# library('gridExtra')
# 
# library('corrplot')
# 
# library('circlize') # for circular plots and colours
# library('cluster')    # clustering algorithms
# library('factoextra') # clustering algorithms & visualization
# library('ggfortify') # so ggplot understands prcomp objects
# library('ape') # for phylogeny plotting
# library('dendextend') # for dendrogram plotting
# library('readxl') # for reading in Excel spreadsheets
# library('plotly')
# library('scales')
# library('processx') # for downloading the plotly plots
# library('cowplot')
# library('ComplexHeatmap')
# library('ggbiplot')
# library('ggpattern')
